---
title: "FINALPRESENTATION"
author: "Alice Wang"
date: "December 6, 2015"
output: pdf_document
---
```{r}
library(png)
require(knitr)
opts_knit$set(root.dir = "/users/alicewang/desktop/stat133/finalproject/images")
```
#GDP vs Years
```{r}
grid::grid.raster(readPNG("1GDPvsYears.png" ))
```
#Damages vs Years
```{r}
grid::grid.raster(readPNG("2DamagesvsYears.png" ))
```
#Most Damaging Natural Disaster per year
```{r}
grid::grid.raster(readPNG("3Most_Damaging_Natural_Disaster_per_Year.png" ))
```
#Pokemon Type vs Power
```{r}
grid::grid.raster(readPNG("../images/4PokemonType_Power.png" ))
```
#Pokemon Type vs Economic Damage
```{r}
grid::grid.raster(readPNG("../images/5PokemonType_EconDamage.png" ))
```
#Pokemon Type vs Casualties
```{r}
grid::grid.raster(readPNG("../images/6PokemonType_Casualties.png" ))
```
#Pokemon per Type
```{r}
grid::grid.raster(readPNG("../images/7Pokemon_per_Type.png" ))
```
#Pokemon Power per Type
```{r}
grid::grid.raster(readPNG("../images/8Pokemon_Power_per_Type.png" ))
```
#Average Pokemon Power per Type
```{r}
grid::grid.raster(readPNG("../images/9Avg_Pokemon_Power_per_Type.png" ))
```
#Disasters per Type
```{r}
grid::grid.raster(readPNG("../images/10Disasters_per_Type.png" ))
```
#Disasters Type per Casualty per Year
```{r}
grid::grid.raster(readPNG("../images/11Disasters_Type_and_Casualties_per_Type.png" ))
```
#Economic Cost vs Natural Disaster
```{r}
grid::grid.raster(readPNG("../images/12Economic_Cost_vs_Disasters.png" ))
```
#Casualty per Disaster
```{r}
grid::grid.raster(readPNG("../images/13Casualties_per_Disaster.png" ))
```
#Economic Cost per Disaster
```{r}
grid::grid.raster(readPNG("../images/14Cost_per_Disaster.png" ))
```
#Disaster Occurrences
```{r}
grid::grid.raster(readPNG("../images/15Disaster_Occurences.png" ))
```
