---
title: "FinalPresentation"
author: "Alice Wang, Jerry Haoming Jiang, Andrew Linxie"
date: "December 3, 2015"
output: pdf_document
---

#Getting the Raw Data

#####Set Working Directory and install packages
####Natural Disasters Data: Cleaning, Organizing and Exporting
```{r}
setwd("/users/alicewang/desktop/stat133/finalproject/")
#install.packages("dplyr")
library(dplyr)
library(readr)
rawnd <- read.csv("./rawdata/naturaldisasters.csv")
types <- c()
type <- as.character(rawnd[,2])
subtype <- as.character(rawnd[,3])
subsubtype <- as.character(rawnd[,11])
for (i in 1:155) {
  if (subsubtype[i] == "--"|| subsubtype[i] == "") {
    if (subtype[i] == "--") {
      types <- c(types, type[i])
    } else if (subtype[i] != "--") {
      types <- c(types, subtype[i])
    }
  } else if (subsubtype[i] != "--") {
    types <- c(types, subsubtype[i])
  }
}
nd <- data.frame("year" = rawnd[,1], "type" = types, "casualty" = rawnd[,5]+rawnd[,6]+rawnd[,7], "cost" = rawnd[,10])

if (!dir.exists("./data")) dir.create("./data") 
file.create("./data/NaturalDisasters.csv")
write.csv(nd,"./data/NaturalDisasters.csv")
```




####Economic Cost Data
#####Process to Cleaning the Economics Data: 
#####1) Reading in the File
```{r}
setwd("/users/alicewang/desktop/stat133/finalproject/")
Raw_GDP <- read.csv("./rawdata/GDP_Data.csv", stringsAsFactors = FALSE,col.names = c("Quarter","GDP"))
```
#####2) Clean Data:
#####I wanted to remove the introductory piece, specifically, where this Data was obtained from (sorry), so that only the numbers remain. 
```{r}
Quarterly_GDP_Data <- Raw_GDP[-1:-10,]
Quarterly_GDP_Data <- data.frame(
                          'Quarter' = Quarterly_GDP_Data[,1], 
                          'GDP' = Quarterly_GDP_Data[,2], stringsAsFactors = FALSE)
Quarterly_GDP_Data[,"GDP"] <- as.numeric(Quarterly_GDP_Data[,"GDP"])
```
#####3) Create Yearly GDP 
```{r}
Annual_GDP_Data <- data.frame(
                      'Years' = 1995:2015,
                      'GDP' = Quarterly_GDP_Data[c(seq(0,nrow(Quarterly_GDP_Data),by = 4),nrow(Quarterly_GDP_Data)),'GDP'])
```
#####4) Export Data
```{r}
setwd("/users/alicewang/desktop/stat133/finalproject/")
if (!dir.exists("./data")) dir.create("./data") 
file.create("./data/Econ.csv")
write.csv(x = Annual_GDP_Data, file = "./data/Econ.csv", row.names = FALSE)

```




###Pokemon Data
Goal: Return a clean data table, types.csv, containing pokemon types, the number of pokemon per type, a power metric for each type, and an average power metric per pokemon for each type

Packages and Working Directory
```{r}
#install.packages("dplyr")
library(dplyr)
library(readr)
```

Getting the Tables we need
```{r}
setwd("/users/alicewang/desktop/stat133/finalproject/")
type_reference <- read_csv("./rawdata/types.csv")
pokemon_stats <- read_csv("./rawdata/pokemon_stats.csv")
pokemon_types <- read_csv("./rawdata/pokemon_types.csv")
stat_names <- read_csv("./rawdata/stat_names.csv")
```

What Types we want
```{r}
types <-  c('water', 'fire', 'flying', 'ground', 'poison', 'dragon', 'dark', 'ice', 'electric', 'rock' )
```

Function to get a type given a type ID. Use the data frame, type_reference
```{r}
get_type_by_id <- function(id) {
  return(type_reference[type_reference$id == id,]$identifier[1])
}
```

Group pokemon_types by first type, get actual types from type ID. Get the number of pokemon per type to get values for the count of each type in our types table. 
```{r}
get_first <- function(arr) {
  return(arr[1])
}
pokemon_id_types <- group_by(pokemon_types, pokemon_id) %>% 
  summarise(type_id = get_first(type_id)) %>%
  mutate(type = sapply(type_id, get_type_by_id)) %>%
  select(-type_id)

type_counts <- group_by(pokemon_id_types, type) %>%
  summarise(pokemon_count = length(pokemon_id)) %>%
  filter(type %in% types)

type_counts

```

Link pokemon_id to types filtered to attack and special attack stats. Add these stats for a power metric. Group by type and add powers to get a total power metric per type
```{r}
stats_and_types <- left_join(pokemon_id_types,pokemon_stats) %>% filter(stat_id %in% c(2,4)) %>% group_by(pokemon_id) %>% summarise(power = sum(base_stat), type = get_first(type))
type_power <- group_by(stats_and_types, type) %>% summarise(total_power = sum(power))
result <- left_join(type_counts, type_power) %>% mutate(avg_power = as.integer(floor(total_power / pokemon_count)))
result
```
Store clean file as types_clean.csv
```{r}
setwd("/users/alicewang/desktop/stat133/finalproject/")
if (!dir.exists("./data")) dir.create("./data") 
file.create("./data/types.csv")
write.csv(x = result, file = "./data/types.csv", row.names = FALSE)

```



##Exploratory Data Analysis and Modelling
###
```{r}
ggplot
```







