---
title: "FinalPresentation"
author: "Alice Wang, Jerry Haoming Jiang, Andrew Linxie"
date: "December 3, 2015"
output: pdf_document
---

#Getting the Raw Data

#####Set Working Directory and install packages
####Natural Disasters Data: Cleaning, Organizing and Exporting
```{r}
setwd("/users/alicewang/desktop/stat133/finalproject/")
#install.packages("dplyr")
library(dplyr)
library(readr)
rawnd <- read.csv("../rawdata/naturaldisasters.csv")
types <- c()
type <- as.character(rawnd[,2])
subtype <- as.character(rawnd[,3])
subsubtype <- as.character(rawnd[,11])
for (i in 1:155) {
  if (subsubtype[i] == "--"|| subsubtype[i] == "") {
    if (subtype[i] == "--") {
      types <- c(types, type[i])
    } else if (subtype[i] != "--") {
      types <- c(types, subtype[i])
    }
  } else if (subsubtype[i] != "--") {
    types <- c(types, subsubtype[i])
  }
}
nd <- data.frame("year" = rawnd[,1], "type" = types, "casualty" = rawnd[,5]+rawnd[,6]+rawnd[,7], "cost" = rawnd[,10])

if (!dir.exists("./data")) dir.create("./data") 
file.create("./data/NaturalDisasters.csv")
write.csv(nd,"./data/NaturalDisasters.csv")
```




####Economic Cost Data
#####Process to Cleaning the Economics Data: 
#####1) Reading in the File
```{r}
setwd("/users/alicewang/desktop/stat133/finalproject/")
Raw_GDP <- read.csv("../rawdata/GDP_Data.csv", stringsAsFactors = FALSE,col.names = c("Quarter","GDP"))
```
#####2) Clean Data:
#####I wanted to remove the introductory piece, specifically, where this Data was obtained from (sorry), so that only the numbers remain. 
```{r}
Quarterly_GDP_Data <- Raw_GDP[-1:-10,]
Quarterly_GDP_Data <- data.frame(
                          'Quarter' = Quarterly_GDP_Data[,1], 
                          'GDP' = Quarterly_GDP_Data[,2], stringsAsFactors = FALSE)
Quarterly_GDP_Data[,"GDP"] <- as.numeric(Quarterly_GDP_Data[,"GDP"])
```
#####3) Create Yearly GDP 
```{r}
Annual_GDP_Data <- data.frame(
                      'Years' = 1995:2015,
                      'GDP' = Quarterly_GDP_Data[c(seq(0,nrow(Quarterly_GDP_Data),by = 4),nrow(Quarterly_GDP_Data)),'GDP'])
```
#####4) Export Data
```{r}
setwd("/users/alicewang/desktop/stat133/finalproject/")
if (!dir.exists("./data")) dir.create("./data") 
file.create("../data/Econ.csv")
write.csv(x = Annual_GDP_Data, file = "./data/Econ.csv", row.names = FALSE)

```




###Pokemon Data
Goal: Return a clean data table, types.csv, containing pokemon types, the number of pokemon per type, a power metric for each type, and an average power metric per pokemon for each type

Packages and Working Directory
```{r}
#install.packages("dplyr")
library(dplyr)
library(readr)
```

Getting the Tables we need
```{r}
setwd("/users/alicewang/desktop/stat133/finalproject/")
type_reference <- read_csv("../rawdata/types.csv")
pokemon_stats <- read_csv("../rawdata/pokemon_stats.csv")
pokemon_types <- read_csv("../rawdata/pokemon_types.csv")
stat_names <- read_csv("../rawdata/stat_names.csv")
```

What Types we want
```{r}
types <-  c('water', 'fire', 'flying', 'ground', 'poison', 'dragon',
            'dark', 'ice', 'electric', 'rock' )
```

Function to get a type given a type ID. Use the data frame, type_reference
```{r}
get_type_by_id <- function(id) {
  return(type_reference[type_reference$id == id,]$identifier[1])
}
```
Function returns the first element of array arr
```{r}
get_first <- function(arr) {
  return(arr[1])
}
```

Group pokemon_types by first type, get actual types from type ID. Get the number of pokemon per type to get values for the count of each type in our types table. 
```{r}
#Table of main pokemon types by pokemon ID
pokemon_id_types <- group_by(pokemon_types, pokemon_id) %>% 
  summarise(
    type_id = get_first(type_id)
    ) %>%
  mutate(
    type = sapply(type_id, get_type_by_id)
    ) %>%
  select(-type_id)

#Number of pokemon by type
type_counts <- group_by(pokemon_id_types, type) %>%
  summarise(
    pokemon_count = length(pokemon_id)
    ) %>%
  filter(type %in% types)

type_counts

```

Link pokemon_id to types filtered to attack and special attack stats. Add these stats for a power metric. Group by type and add powers to get a total power metric per type
```{r}
#Create table containing pokemon types and their corresponding attack and special
# attack stats (combined in a column called power)
stats_and_types <- left_join(pokemon_id_types, pokemon_stats) %>%
  filter(stat_id %in% c(2,4)) %>%
  group_by(pokemon_id) %>% 
  summarise(
    power = sum(base_stat), type = get_first(type)
    )

#Create table with type corresponding to the total sum of all pokemon with the type
type_power <- group_by(stats_and_types, type) %>%
  summarise(total_power = sum(power))

#Join our power table with our count table by type. This is the final result
result <- left_join(type_counts, type_power) %>%
  mutate(
    avg_power = as.integer(floor(total_power / pokemon_count))
    )

result
```

Add a table of colors into pokemon table
```{r}
result$color <- c('black', 'turquoise', 'yellow', 'red', 'maroon', 'brown', 'white', 'purple', 'grey', 'blue')
```

Store clean file as types_clean.csv
```{r, eval = FALSE}
setwd("/users/alicewang/desktop/stat133/finalproject/")
if (!dir.exists("./data")) dir.create("./data") 
file.create("../data/types.csv")
write.csv(x = result, file = "../data/types.csv", row.names = FALSE)

```



##Exploratory Data Analysis and Modelling
###
Packages
```{r}
#install.packages("ggplot2")
library(ggplot2)
```

First, import the tables
```{r}
pokemon_types <- read_csv("../data/types.csv")
natural_disasters <- read_csv("../data/NaturalDisasters.csv")
economic_data <- read_csv("../data/Econ.csv")
```

###Exploratory analysis of the pokemon Dataset
####Number of pokemon per type
```{r}
ggplot(data = pokemon_types, aes(type, pokemon_count, fill = type)) + geom_bar(stat = "identity") + scale_fill_manual(values = pokemon_types$color)
```

From here, we can see that there is an overwhelming amount of water pokemon in the world and not that many flying types. All the other types have pretty much the same amount of pokemon.

####Total Destructive Power of pokemon per type
```{r}
ggplot(data = pokemon_types, aes(type, total_power, fill = type)) + geom_bar(stat = "identity") + scale_fill_manual(values = pokemon_types$color)
```

This looks relatively the same as the last plot. It seems that no matter what type, it is strength in numbers that prevail for the total amount of data 

####Average Destructive Power of Pokemon per Type
```{r}
ggplot(data = pokemon_types, aes(type, avg_power, fill = type)) + geom_bar(stat = "identity") + scale_fill_manual(values = pokemon_types$color)
```

Now we see a different trend. It seems that now dragon types have the most average power per pokemon. Most of the other types have a power metric around 150 units.

###Exploratory analysis of Natural Disasters Data Set
Let's first plot the occurrences of natural disasters per year
```{r}
occurrences <- group_by(natural_disasters, year) %>% summarise(count = length(casualty))
ggplot(data = occurrences, aes(year, count)) + geom_line() + geom_point() + labs(x = "year", y = "occurences", xlim = seq(1995,2016))
```
From this we see a steady rise and fall in natural disasters in the US over the years.
Let's now plot the number of casualties from natural disasters per year
```{r}
ggplot(data = natural_disasters, aes(year, casualty)) + geom_bar(stat = "identity") 
```
Wow, it looks like 2008 had an abnormally large amount of casualties from natural disasters over the years. 
Let's now plot the economic cost of natural disasters over the years.
```{r}
ggplot(data = natural_disasters, aes(year, cost)) + geom_bar(stat = "identity")
```
It looks like 2005 has one of the greatest economic cost from disasters. This is possibly from the occurrences of hurrican katrina. It is also interesting to note how although the number of casualties in 2008 was abnormally high, the economic cost was not as great.
Let's see the most casualties affected by each disaster
```{r}
ggplot(data = natural_disasters, aes(type, casualty)) + geom_bar(stat = "identity")
```
From this, it can be seen a bulk of the disasters stem from fires.
Now, let's assess economic cost per disaster.
```{r}
ggplot(data = natural_disasters, aes(type, cost)) + geom_bar(stat = "identity")
```
It seems that forest fires had an abnormally large amount of costs compared with the other types of disasters



